On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 blind.tex
Start rewriting blind sampbqp
Make flow of blind then fully classical consistent

Now we're ready to construct our delegation protocol.

\begin{algorithm}
	\caption{Verifiable, secure, and constant round delegation}
	\label{ProtoPriv}
	\begin{algorithmic}[1]
		\Procedure{Delegation}{C, x}
			\State Compute $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{QHE.Eval}_{evk}(C, \tilde{x})$
			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
			\State Request $\Lambda'$ based on \autoref{decodeMeasureOrder}, where $\Lambda$ is the basis choice if $C(x)$ were delegated.
			\State Let $y$ be the measurement results from the server
			\State \Return $\widehat{\mathsf{QHE.Dec}_{sk}}(y)$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{thm}
    \label{QPIP1thm}
	\myprotoref{ProtoPriv} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
\end{thm}
\begin{proof}
	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.

>>>>

Now we compile our $\QPIP_1$ protocol \myprotoref{protoQPIP1} using the quantum homomorphic encryption $\mathsf{QHE}$ \Ethan{TODO maybe wrap this as a def} in a similar way as what we did for our blind $\BQP$ delegation protocol in \cref{sec:BlindQBP}

The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis.

\begin{thm}
	Compiling \cref{proto:QPIP0samp} using $\mathsf{QHE}$ preserves its completeness and soundness.
\end{thm}
\begin{proof}
	A honest prover still gets accepted with overwhelming probability by the correctness of $\mathsf{QHE}$. \Ethan{Not sure if too hand-wavy}

	\Ethan{Check how much of the following still applies before erasing}
	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.

### 2020-02-02 preliminaries.tex
Start rewriting blind sampbqp
Make flow of blind then fully classical consistent

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.

$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$

@@

>>>>

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda, 1^D)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $D$.

@@

In general, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then this can be used as a compiler to achieve blindness.
